Understanding Cannabis Usage in Canada: Consistent Demographic Patterns in Cannabis Use Across Canada May Positively Correlate to High Frequency Use

### 2023-04-18 outputs/paper/paper.qmd
push simulated data

## Data Management {#sec-first-point}

## Source {#sec-second-point}

## Sampling {#sec-third-point}

## Key Features {#sec-fourth-point}

>>>>

## Data Management {#sec-first-point}
This paper utilizes the R statistical programming language [@citeR], along with packages tidyverse [@citetidyverse], here [@citehere], janitor [@citejanitor], and dplyr [@citedplyr]. The figures in this paper have been created using ggplot2 [@citeggplot2] and the tables have been created using knitr [@citeknitr] and kableExtra [@citekablextra]. The color styles in graphs have been created using the RColorBrewer packages [@citercolorbrewer].

## Source {#sec-second-point}
This paper uses data extracted from the Public Use Microdata File (PUMPF) for the 2021 Canadian Tobacco and Nicotine Survey (CTNS). The CTNS is a national survey conducted by Health Canada to collect information about the prevalence of cigarette smoking, vaping, and cannabis use in Canada. Until 2017, Statistics Canada administered the Canadian Tobacco, Alcohol and Drugs Survey (CTADS), which gathered information on the use of tobacco, alcohol, and drug use across Canada [@citectnspumf]. However, in 2019, the Canadian Alcohol and Drugs Survey (CADS) was carried out specifically to collect data on alcohol and drug use, separately from the Canadian Tobacco and Nicotine Survey (CTNS), which is focused mainly on gathering data on tobacco and nicotine use, including cannabis [@citectnspumf].

The PUMPF is a dataset that contains anonymized, individual-level data from the CTNS [@citectnspumf]. It is a subset of the full survey dataset that involves balancing the preservation of respondent confidentiality and providing the most useful data which is then made available to researchers and analysts who require access to detailed information on tobacco, nicotine, and cannabis use in Canada [@citectnspumf]. The CTNS PUMF includes information on a wide range of variables, including frequency of use, attitudes and beliefs, and use of cessation aids [@citectnspumf]. It also includes demographic variables such as age, gender, and province of residence [@citectnspumf].

Data collection for the 2022 reference period was conducted from December 1, 2020 to May 3, 2021, and was gathered directly and voluntarily from survey respondents either through an electronic questionnaire (EQ) or through CATI (computer- assisted telephone interviewing) [@citectnsinfo]. The 2021 CTNS electronic questionnaire was developed in consultation with Health Canada, and underwent a process of cognitive testing through in-depth interviews conducted by Statistics Canada's Questionnaire Design Resource Centre to test the survey content in both of Canada's official languages [@citectnsinfo].

## Sampling {#sec-third-point}
The CTNS is designed to provide a comprehensive picture of tobacco, nicotine, and cannabis use, attitudes, and behaviours among non-instituionalized Canadians ages 15 years and older who are not members of collectives or living on reserves [@citectnsinfo]. The survey has a stratified sample and cross-sectional design with sampling units: individuals aged 15 to 24 and individuals aged 25 and older [@citectnsinfo]. For the former (individuals aged 15 to 24), the CTNS sample has a one-stage desion, and the individual is the sampling unit [@citectnsinfo]. For the latter (individuals aged 25 and older), the CTNS sample has a two-stage design where the sampling unit for the first stage is the dwelling, and the sampling unit for the second stage is the individual [@citectnsinfo]. The CTNS used different methods for stratification. For those aged 15 to 24, the sample was stratified by age group and province, with a systematic sample selected independently for each group [@citectnsinfo]. For those aged 25 and older, the sample was stratified by province and a simple random sample of dwellings was selected [@citectnsinfo]. In terms of sampling and subsampling, the survey allocated samples to produce province-level and region-level estimates for the age groups. The initial sample size was 12,000 individuals aged 15-24 and 15,000 dwellings for those aged 25 and older [@citectnsinfo]. The survey sent an initial sample of 27,000 dwellings or individuals for collection [@citectnsinfo].

## Key Features {#sec-fourth-point}
This paper investigates the relationship between demographic factors and cannabis use in Canada. More specifically, it explores the estimand, how does characteristics such as user age, gender, and region correlate with cannabis consumption methods (smoking, vaping, taking edibles) and their respective frequencies of usage in Canada. In my analysis, I removed

(not right) -->2,164 responses to account for unanswered or not applicable responses. We did this to ensure that the data used in this paper is complete and representative of all variables. The variables we selected for our analysis can be seen in @tbl-1 and their measurement levels can be seen in @tbl-2. Responses were measured using Likert scales which measured respondents' opinions to the questions being asked.
